\documentclass{memoir}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{listings}

\begin{document}
	
	\title{The TOOG Software Import Specification Format}
	\maketitle
	\tableofcontents
	\pagebreak
	\author{Daniel Thornton}
	\section{Introduction}
	
	\subsection{What Is TOOG?}
	TOOG is a customer relations management system, quoting package, and more. TOOG allows users to create and manage jobs, customers, suppliers, pricing, and quotes. Users can currently import their jobs from third-party packages using the CSV import system from within the TOOG web application. This feature enables the creation of items from an existing job with their requisite inventory items and manufactured parts, which are then used to generate a quote for customers. TOOG aims to streamline this process by providing a service that allows third-party desktop applications to integrate closely with TOOG through a service or daemon available on Windows, GNU-Linux, and Mac.
	
	\subsection{TOOG Software Import Service}
	The TOOG Import service and its companion libraries provide functions for third-party applications to connect to TOOG. These libraries facilitate job creation, collections, and item management locally without needing direct interaction with TOOG, simplifying third-party software integration. There are three methods to connect with the TOOG Import service:
	
	\begin{itemize}
		\item Manual connection using a named pipes.
		\item Communication via the Windows native DLL (TOOG.Import.dll and TOOG.Import.h) (available soon)
		\item Communication via the .NET Core class library (TOOG.Import.dll), implemented in .NET (coming soon)
	\end{itemize}
	
	It is recommended to use the Windows native DLL for Windows systems due to its superior performance and broader support. The .NET Core class library is intended for multi-platform applications or those developed in .NET.
	
	\section{Important Concepts}
	
	\subsection{Document Hierarchy}
	Understanding TOOG's internal object hierarchy is crucial when creating imports. The hierarchy is as follows:
	\begin{quote}
		\textit{Account → Site → Job → Collection → Item}
	\end{quote}
	When interfacing with TOOG, you must create or reference a job and collection to import data.
	
	\subsection{Accounts}
	For using the TOOG Software Import Service, an in-depth understanding of the Account object is not required. The service provides a method to fetch a list of current TOOG customers, each with their account name, ID, and basic contact information. When creating a Job, you must include the ID of the account for which the user wants to create the Job. If this ID is not provided, creation will fail.
	
	\subsection{Sites}
	Sites are associated with Accounts and act as parent entities for Job lists. Sites are automatically generated when an account is created in TOOG, but users can also create their own Sites. When fetching accounts, TOOG returns a flattened list of Sites, where the account name is prefixed to the site name (e.g., Account1/Site1). This structure helps to separate accounts or present them to the user as needed. The provided ID corresponds to the Site and is necessary when creating a Job, as the Site is the direct parent of the Job, not the Account.
	
	\subsection{Job Lists}
	A Job represents a task or assignment for a client, storing details such as the job number and contact person. When creating a Job, you must provide the required fields and ensure that the site ID is included.
	
	\subsection{Import Types}
	
	Import Types in TOOG enable the importing of data from a wide range of applications. TOOG maps columns from a CSV file to internal attributes and inventory items, creating new items within a job based on data exported from third-party applications. Import Types support the following special columns and Properties:
	
	\begin{enumerate}[]
		\item \textbf{Name}\\
		\textit{The name that the newly created item will use, e.g., "End Left".}
		
		\item \textbf{Quantity}\\
		\textit{The quantity of the item to be created during the import. Note: Creating with a quantity of X does not create multiple items.}
		
		\item \textbf{Blueprint}\\
		\textit{Specifies the type of item to create, such as a cabinet, part, or similar.}
		
		\item \textbf{Common Item Prefix}\\
		\textit{Sets a prefix for all common item properties.}
		
		\item \textbf{Common Item Column}\\
		\textit{Allows you to import items as children of a "common item," with the parent being the common item. This name should be unique across parents but shared among children. For example:}
		
		A cabinet with the following structure:
		
		\begin{verbatim}
			{
				"cabinet1": {
					"name": "floor two-door",
					"parts": [
					{
						"name": "end left"
					},
					{
						"name": "end right"
					}
					]
				},
				"cabinet2": {
					"name": "floor two-door",
					"parts": [
					{
						"name": "end left"
					},
					{
						"name": "end right"
					}
					]
				}
			}
		\end{verbatim}
		
		In this example, "cabinet1" and "cabinet2" are common items, and each child part (e.g., "end left" or "end right") is associated with its respective common item ("cabinet1" or "cabinet2"). The common item prefix is used to set up properties for the common item (e.g., quantity). For instance, if your quantity column is "qty" and you use a common item prefix of "cab", TOOG would look for the "cabqty".
		
		\item \textbf{Group}\\
		\textit{Groups items together as needed (within a common item)}
	\end{enumerate}
	
	\subsection{Import Types}
	
	Import Types in TOOG enable the importing of data from a wide range of applications. TOOG maps columns from a CSV file to internal attributes and inventory items, creating new items within a job based on data exported from third-party applications. Import Types support the following special columns:
	
	\begin{enumerate}[]
		\item \textbf{Name}\\
		\textit{The name that the newly created item will use, e.g., "Floor standard 200".}
		
		\item \textbf{Quantity}\\
		\textit{The quantity of the item to be created during the import. Note: Creating with a quantity of X does not create multiple items but rather sets their qty.}
		
		\item \textbf{Blueprint}\\
		\textit{Specifies the type of item to create, such as a cabinet, part, or similar.}
		
		\item \textbf{Common Item Prefix}\\
		\textit{Sets a prefix for all common item properties.}
		
		\item \textbf{Common Item Column}\\
		\textit{Allows you to import items as children of a "common item," with the parent being the common item. This name should be unique across parents but shared among children. For example:}
		
		A cabinet with the following structure:
		
		\begin{verbatim}
			{
				"cabinet1": {
					"name": "floor two-door",
					"parts": [
					{
						"name": "end left"
					},
					{
						"name": "end right"
					}
					]
				},
				"cabinet2": {
					"name": "floor two-door",
					"parts": [
					{
						"name": "end left"
					},
					{
						"name": "end right"
					}
					]
				}
			}
		\end{verbatim}
		
		In this example, "cabinet1" and "cabinet2" are common items, and each child part (e.g., "end left" or "end right") is associated with its respective common item ("cabinet1" or "cabinet2"). The common item prefix is used to set up properties for the common item (e.g., quantity). For instance, if your quantity column is "qty" and you use a common item prefix of "cab", TOOG would look for "cabqty".
		
		\item \textbf{Group}\\
		\textit{Groups items together as needed.}
	\end{enumerate}
	\subsection{Import Line Items}
	\subsection{Quoting}
	
	\subsection{Inventory Management \& Attributes}
	\pagebreak
	
	\section{Manually Connecting to the Import Service Via Named Pipes}
	
	The TOOG service uses named pipes for communication normally you should connect via the provided libraries however if required, this section outlines the process for connecting to the TOOG service, sending the required data, and interacting with the service.
	
	\subsection{Connection Process}
	
	\subsubsection{Establishing Initial Connection}
	\begin{enumerate}
		\item \textbf{Create a Named Pipe Client:} Initialize a named pipe client to connect to the TOOG service with the pipe name "TOOGSoftwareImportService.pipe".
		\item \textbf{Connect to the Pipe:} Establish a connection to the named pipe server.
	\end{enumerate}
	
	\subsubsection{Sending Initial Data}
	\begin{enumerate}
		\item \textbf{Prepare the API Key Message:} Send a message containing the API key for authentication. The message should have the following details:
		\begin{itemize}
			\item \textbf{Message Type:} \texttt{none}
			\item \textbf{Message Format:} \texttt{utf8}
			\item \textbf{Message Body:} The API key as a string
		\end{itemize}
		\item \textbf{Send the Message:} Transmit the API key message to the TOOG service.
	\end{enumerate}
	
	\subsubsection{Handling Service Response}
	\begin{enumerate}
		\item \textbf{Receive Session Pipe Name:} After sending the API key, the service will respond with a new pipe name for the session. Extract this session pipe name from the response.
		\item \textbf{Disconnect from Initial Pipe:} Close the initial pipe connection once the session pipe name is received.
	\end{enumerate}
	
	\subsubsection{Communicating via Session Pipe}
	\begin{enumerate}
		\item \textbf{Create New Named Pipe Client:} Use the session pipe name received to initialize a new named pipe client for ongoing communication.
		\item \textbf{Connect to Session Pipe:} Establish a connection to the session pipe.
		\item \textbf{Send and Receive Messages:} Use the session pipe to send and receive messages according to the service's protocol. The message format and types should be as follows:
		\begin{itemize}
			\item \textbf{Message Type:} Specify the type of message (e.g., \texttt{startImport}, \texttt{queryJobs}).
			\item \textbf{Message Format:} Specify the format of the message body (e.g., \texttt{utf8}).
			\item \textbf{Message Body:} The actual data to be transmitted.
		\end{itemize}
	\end{enumerate}
	
	\subsubsection{Closing the Connection}
	\begin{enumerate}
		\item \textbf{Dispose of Named Pipe Client:} After completing communication, properly dispose of the named pipe client to free resources.
	\end{enumerate}
	
	\section{Example Communication Flow}
	\begin{enumerate}
		\item Initialize a named pipe client and connect to "TOOGSoftwareImportService.pipe".
		\item Send an API key with \texttt{MessageType.none} and \texttt{MessageFormat.utf8}.
		\item Receive the session pipe name from the service and disconnect from the initial pipe.
		\item Create a new named pipe client using the session pipe name and connect.
		\item Send and receive messages according to the service protocol.
		\item Dispose of the named pipe client after communication is complete.
	\end{enumerate}
	
	\section{Message Overview}
	
	\subsection{Message Structure}
	A \texttt{Message} in the TOOG Import Service is a structured data packet used for communication between the client and server. It consists of a header and a body.
	
	\subsubsection{Header}
	The header contains metadata about the message and is composed of the following fields:
	\begin{itemize}
		\item \textbf{Message Format (4 bytes):} Indicates the format of the message data. Possible formats and their 4-byte representations are:
		\begin{itemize}
			\item \texttt{None} (0): \texttt{00 00 00 00}
			\item \texttt{utf8} (1): \texttt{00 00 00 01}
			\item \texttt{image\_bmp} (2): \texttt{00 00 00 02}
			\item \texttt{image\_png} (3): \texttt{00 00 00 03}
			\item \texttt{image\_jpg} (4): \texttt{00 00 00 04}
			\item \texttt{raw} (5): \texttt{00 00 00 05}
		\end{itemize}
		\item \textbf{Message Type (4 bytes):} Specifies the type of message. Example values and their 4-byte representations are:
		\begin{itemize}
			\item \texttt{none} (0): \texttt{00 00 00 00}
			\item \texttt{startImport} (1): \texttt{00 00 00 01}
			\item \texttt{lineItem} (2): \texttt{00 00 00 02}
			\item \texttt{endImport} (3): \texttt{00 00 00 03}
			\item \texttt{queryAccounts} (4): \texttt{00 00 00 04}
			\item \texttt{queryJobs} (5): \texttt{00 00 00 05}
			\item \texttt{queryImportTypes} (6): \texttt{00 00 00 06}
		\end{itemize}
		\item \textbf{Message ID (16 bytes):} A unique identifier for the message used for tracking and error reporting.
		\item \textbf{Message Length (4 bytes):} The length of the message body, which helps determine how many bytes to read. Example values and their 4-byte representations are:
		\begin{itemize}
			\item \texttt{0} bytes: \texttt{00 00 00 00}
			\item \texttt{256} bytes: \texttt{00 00 01 00}
			\item \texttt{1024} bytes: \texttt{00 00 04 00}
		\end{itemize}
	\end{itemize}
	
	The header fields are sequentially ordered within the first 22 bytes of the message:
	\begin{itemize}
		\item Bytes 0-3: Message Format
		\item Bytes 4-7: Message Type
		\item Bytes 8-23: Message ID
		\item Bytes 24-27: Message Length
	\end{itemize}
	
	\subsubsection{Body}
	The body of the message starts at byte offset 0x22 (34 in decimal) and contains the actual data being transmitted. The content and format of the body depend on the message type and format specified in the header. For example:
	\begin{itemize}
		\item For a text message, the body would be a UTF-8 encoded string (typically JSON).
		\item For an image message, the body would contain binary data of the image file.
	\end{itemize}
	
	When creating or parsing a message, ensure the header fields are properly set and that the body conforms to the expected format for the specified message type.
	
	In summary, a \texttt{Message} consists of a header with metadata (format, type, ID, and length) and a body containing the actual data. Proper structuring and interpretation of these components are crucial for effective communication within the TOOG Import Service.
	
	
	\section{Message Content And Service Responses}
	TOOG Import Service server can send data to the client below describes the different message types, their content, and their usage in the communication between the server and client.
	
	\section{Message Types}
	
	\subsection{ImportTypesResponse}
	The \texttt{ImportTypesResponse} message provides details about the import types available in the system. It includes:
	\begin{itemize}
		\item \textbf{ImportTypes}: A list of available import types. Each import type contains:
		\begin{itemize}
			\item \textbf{Id}: The unique identifier for the import type.
			\item \textbf{Name}: The name of the import type.
			\item \textbf{Columns}: An array of column names associated with the import type.
			\item \textbf{CommonItemPrefix}: A common prefix used for items in this import type.
		\end{itemize}
		\item \textbf{DefaultImportTypeId}: The identifier of the default import type.
	\end{itemize}
	
	\subsection{Job}
	The \texttt{Job} message provides information about jobs in the system. It includes:
	\begin{itemize}
		\item \textbf{Jobs}: A list of jobs. Each job contains:
		\begin{itemize}
			\item \textbf{Id}: The unique identifier of the job.
			\item \textbf{Name}: The name of the job.
			\item \textbf{JobStatusId}: The identifier of the job status.
			\item \textbf{JobNumber}: The number associated with the job.
			\item \textbf{SiteId}: The identifier of the site where the job is located.
			\item \textbf{Collections}: A list of collections associated with the job.
		\end{itemize}
		\item \textbf{JobStatuses}: A list of job statuses. Each status contains:
		\begin{itemize}
			\item \textbf{Id}: The unique identifier of the job status.
			\item \textbf{Name}: The name of the job status.
		\end{itemize}
	\end{itemize}
	
	\subsection{Site}
	The \texttt{Site} message provides information about sites. It includes:
	\begin{itemize}
		\item \textbf{Url}: The URL of the site.
		\item \textbf{Sites}: A list of sites. Each site contains:
		\begin{itemize}
			\item \textbf{Id}: The unique identifier of the site.
			\item \textbf{Name}: The name of the site.
			\item \textbf{AccountId}: The identifier of the account associated with the site.
			\item \textbf{Details}: The details of the site, including:
			\begin{itemize}
				\item \textbf{Address1}: The first line of the address.
				\item \textbf{Address2}: The second line of the address.
				\item \textbf{Address3}: The third line of the address.
				\item \textbf{City}: The city of the site.
				\item \textbf{State}: The state of the site.
				\item \textbf{Zip}: The ZIP code of the site.
				\item \textbf{Country}: The country of the site.
			\end{itemize}
		\end{itemize}
		\item \textbf{JobStatuses}: A list of job statuses available at the site.
	\end{itemize}
	
\end{document}
